R Packages to Aid in Handling Web Access Logs

### 2015-12-26 paper/paper.Rmd
copyedit, improve

A vector of URLs passed into `url_parse` produces a data.frame, with one column for each of the IETF-supported components, and empty strings representing components that could not be found. Additionally, influenced by the style of the *lubridate* package \citep{lubridate}, `urltools` contains functions to get or *set* individual components:

@@

As a result of this functionality, urltools provides a package to make URL manipulation faster, easier and far more accessible, reducing the burden associated with munging access logs or similar datasets and allowing a researcher to get to the statistical analysis faster.

@@

With these concerns in mind, we wrote the \CRANpkg{rgeolocate} package. Through \pkg{httr} this contains convenient, vectorised bindings
to various web services that provide geographic metadata about IP addresses. More importantly, using the \CRANpkg{Rcpp} package to integrate C++ and R, \pkg{rgeolocate} also features a direct, compiled binding to the MaxMind API. This means that local binary databases can also be queried, which is far faster and more robust than web-based equivalents and avoids the privacy concerns associated with transmitting users' IP addresses externally.

>>>>

A vector of URLs passed into \code{url\_parse} produces a data.frame, with one column for each of the IETF-supported components, and empty strings representing components that could not be found. Additionally, influenced by the style of the \CRANpkg{lubridate} package \citep{lubridate}, \pkg{urltools} contains functions to get or *set* individual components:

@@

As a result of this functionality, \pkg{urltools} makes URL manipulation faster, easier and far more accessible, reducing the burden associated with munging access logs or similar datasets and allowing a researcher to get to the statistical analysis faster.

@@

With these concerns in mind, we wrote the \pkg{rgeolocate} package. Through \pkg{httr} this contains convenient, vectorised bindings
to various web services that provide geographic metadata about IP addresses. More importantly, using the \CRANpkg{Rcpp} package to integrate C++ and R, \pkg{rgeolocate} also features a direct, compiled binding to the MaxMind API. This means that local binary databases can also be queried, which is far faster and more robust than web-based equivalents and avoids the privacy concerns associated with transmitting users' IP addresses externally.
